---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# qmdtemplates

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

## Overview

`qmdtemplates` enables convenient storage and loading of custom [Quarto](https://quarto.org/) templates.

## Installation

Install `qmdtemplates` from GitHub:

```{r eval=FALSE}
# install.packages("remotes")
remotes::install_github("kthayashi/qmdtemplates")
```

Alternatively, fork this GitHub repo to add your own templates.

## Usage

`qmdtemplates` is comprised of two main functions, both of which are intended to be used interactively as part of one's project workflow (analogous to the `[usethis](https://usethis.r-lib.org/)` package).

Check available templates with `qmdtemplates::available()`:

```{r}
qmdtemplates::available()
```

Use a template (i.e. copy it into a target directory) with `qmdtemplates::use()`:

```{r eval=FALSE}
qmdtemplates::use("manuscript.docx")
```

## Disclaimers

This package is neither associated with nor endorsed by the Quarto open source project.
