---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# qmdtemplates

<!-- badges: start -->
[![R-CMD-check](https://github.com/kthayashi/qmdtemplates/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/kthayashi/qmdtemplates/actions/workflows/R-CMD-check.yaml)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

## Overview

`qmdtemplates` enables convenient storage and loading of custom [Quarto](https://quarto.org/) templates.

## Installation

Install `qmdtemplates` from GitHub:

```{r eval=FALSE}
# install.packages("remotes")
remotes::install_github("kthayashi/qmdtemplates")
```

Alternatively, fork this GitHub repo to customize/add templates.

## Usage

`qmdtemplates` is comprised of two main functions, both of which are intended to be used interactively as part of one's project setup.

Check available templates with `qmdtemplates::available()`:

```{r}
qmdtemplates::available()
```

Use a template (i.e. copy it into a target directory) with `qmdtemplates::use()`:

```{r include=FALSE}
if (!dir.exists("assets")) dir.create("assets")
```

```{r}
qmdtemplates::use("manuscript.docx", at = "assets")
```

```{r include=FALSE}
unlink("assets", recursive = TRUE)
```

## Disclaimers

This package is neither associated with nor endorsed by the Quarto open source project.
